---
title: "Mieszko"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

dane <- apartments_rent_pl_2024_06
View(dane)

install.packages("mice")
library(mice, warn.conflicts = FALSE)



md.pattern(dane)

library(dplyr)
dane <- dane %>% select(-id)

View(dane)

imputed <- mice(dane, m = 5, method = 'pmm', seed = 123)
completed_data <- complete(imputed, 1)
View(completed_data)

color <-  c("red", "green", "blue", "blue", "red")
df    <-  data.frame(color)

df$color <-  as.integer(factor(df$color))

dane$type <- as.integer(factor(dane$type))
$typetypedane$type, m=5, maxit=50, meth=c("polr", "", "", ""), seed=500)

completed_data <- complete(imputed, 1)
View(completed_data)


dane$buildingMaterial <- as.integer(factor(dane$buildingMaterial))
imputed <- mice(dane, m = 5, method = 'lda', seed = 123)

completed_data <- complete(imputed, 1)
View(completed_data)

